\chapter{Configurations}

\subsection{Core Parameters}

The size and implementation style of the PLIC module is defined via HDL
parameters as specified below:

\begin{longtable}[c]{@{\extracolsep{\fill}}lccl@{}}	
	\toprule 
	\textbf{Parameter} & \textbf{Type} & \textbf{Default} & \textbf{Description}\\
	\midrule
	\endhead
	\emph{\textbf{AHB Interface:}}\\
	\texttt{HADDR\_SIZE} & Integer & 32 & Width of AHB Address Bus\\
	\texttt{HDATA\_SIZE} & Integer & 32 & Width of AHB Data Buses\\
	\\
	\emph{\textbf{PLIC Configuration:}}\\
	\texttt{SOURCES} & Integer & 16 & Number of Interrupt Sources\\
	\texttt{TARGETS} & Integer & 4 & Number of Interrupt Targets\\
	\texttt{PRIORITIES} & Integer & 8 & Number of Priority Levels\\
	\texttt{MAX\_PENDING\_COUNT} & Integer & 8 & Max number of pending events\\
	\texttt{HAS\_THRESHOLD} & Integer & 1 & Is Threshold Implemented\\
	\texttt{HAS\_CONFIG\_REG} & Integer & 1 & Is Config Reg. Implemented\\
	\bottomrule 	
	\caption{Core Parameters}
	\label{tab:CoreParams}
\end{longtable}

\subsection{HADDR\_SIZE}

The \texttt{HADDR\_SIZE} parameter specifies the address bus size to
connect to the AHB-Lite based host. Valid values are 32 and 64. The
default value is 32.

\subsection{HDATA\_SIZE}

The \texttt{HDATA\_SIZE} parameter specifies the data bus size to
connect to the AHB-Lite based host. Valid values are 32 and 64. The
default value is 32

\hypertarget{SOURCES}{\subsection{SOURCES}\label{sec:SOURCES}}

The \texttt{SOURCES} parameter defines the number of individual
interrupt sources supported by the PLIC IP. The default value is 16. The
minimum value is 1.

\hypertarget{TARGETS}{\subsection{TARGETS}\label{sec:TARGETS}}

The \texttt{TARGETS} parameter defines the number of targets supported
by the PLIC IP. The default value is 4. The minimum value is 1.

\subsection{PRIORITIES}

\sloppy
The PLIC IP supports prioritisation of individual interrupt sources. The \texttt{PRIORITIES} parameter defines the number of priority levels supported by the PLIC IP. The default value is 8. The minimum value is 1.

\subsection{MAX\_PENDING\_COUNT}

\sloppy
The PLIC module supports multiple concurrently arriving interrupt
requests. The maximum number of requests that are supported is defined
by the \texttt{MAX\_PENDING\_COUNT} parameter.\todo{Expand MAX\_PENDING\_COUNT explanation}

\begin{comment}
This is unclear.
The MAX_PENDING_COUNT parameter determines how many edge triggered interrupts can be queued. This is per interrupt-source. Each interrupt-source has an interrupt-pending-counter. MAX_PENDING_COUNT indicates the max.number this counter can hold.
If there are more interrupts pending than the counter can hold, then the counter retains its value (ie it 'hit' a ceiling).
The minimum value, of course, is 0, which indicates no pending interrupt.
\end{comment}

The default value is 8. The minimum value is 0.

\subsection{HAS\_THRESHOLD}

The PLIC module supports interrupt thresholds -- the masking of
individual interrupt sources based on their priority level. The
\texttt{HAS\_THRESHOLD} parameter defines if this capability is enabled.

The default value is enabled (`1'). To disable, this parameter should be
set to `0'.

\subsection{HAS\_CONFIG\_REG}

The PLIC module supports an optional Configuration Register, which is
documented in section 0. The \texttt{HAS\_CONFIG\_REG} parameter defines
if this capability is enabled.

The default value is enabled (1'). To disable this parameter should be
set to `0'.
